Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-05-31 paper/paper.tex
#20 add skeleton of minimal lit review

\title{Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}
}
\author{Elias Hadj Ammar}
\date{May 2023}

@@

>>>>

\title{Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback. I thank Matthias Weigand in particular for providing me with his own data and for pointing me towards the paper by \cite{schoenholzer2018}.}
}
\author{Elias Hadj Ammar}
\date{May 2023}

@@

\section{Literature review}

A seminal paper is that of \cite{as1997}. It suggests a theoretical model for determining the optimal size and number of states. The authors model the tradeoff between BLANK and BLANK.

More recently, a lot of empirical research has been done using city-level historical data and investigating the effects of Europe's political landscape on the economy. In a way, this started with the Neo-Institutionalists - e.g. \cite{delong1993}, who investigate the effect of absolutist vs non-absolutist rule and find that self-governance is advantageous.

\cite{diamond1997} discusses some ways in which the geography of a place, via its geopolitical implications, can affect the long-run development of civilisation: he contrasts remote and unified China with geographically and politically fragmented Europe, suggesting that BLANK.

\cite{cervellati2022} provide a very rich survey of the literature on the state system in pre-industrial Europe. They also provide empirical evidence for BLANK.

The next big thing in the economic history literature appears to be fiscal capacity. I'm not yet sure how that is relevant to my project, but I feel like I ought to mention it.

Finally, \cite{schoenholzer2018} are the closest paper to this one. They ask a very similar question: How does switching between states affect long-run urban growth? To answer this, they do BLANK. They find that BLANK. The present project differs from theirs in a few ways: firstly, conflict is explicitly part of their analysis; it is part of what causes the tradeoff between short-run costs and long-run benefits. In my survey, conflict is merely a confounder whose effect I wish to exclude.

2-3 pubs each on
public goods provision
transaction costs
strategic motives
